On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Cosmetics

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
alothough the set is of characteristic 1,
it cannot be extended by reflecting relatively to the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.

%TODO: write about points which prevent the set from reflection

$\mathcal{P}_8=
\sqrt{1}/13*
\{
( 29575 ; 0);
( -2366 ; -8112);
( 12844 ; 0);
( 10647 ; -14196);
( 8450 ; 0);
( 15022 ; -3696);
( 21294 ; 0);
( 0 ; 0);
\}
$

\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/8_2535_1_d680ff2d172ebe40250a54ca9419af34_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

@@

\section{Final remarks}
All the given planar integral point sets were obtained through a combination of computer search and intuition of the authors.
The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo

>>>>

Figure~\ref{8_2535_1_d680} displays an IPS with
no axis of symmetry;
although the set is of characteristic 1,
it cannot be extended by reflecting relatively to the $x$ axis.
Moreover, we failed to extend it by dilation and looking for extra points on the $x$ axis.
%
%TODO: write about points which prevent the set from reflection
%
\begin{multline}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{multline}
%
\begin{figure}[h!]
\center{\includegraphics[width=1\linewidth]{./img/8_2535_1_d680ff2d172ebe40250a54ca9419af34_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

@@

\section{Final remarks}
All the given planar integral point sets were obtained through a combination of computer search and intuition of the authors.

The source code can be obtained at https://gitlab.com/Nickkolok/ips-algo
